### 2018-03-22 Paper/jaccardbaetica.tex
update introduction

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. They allows us to highlight a part of mechanism of production and distribution of goods between different communities.

@@

The production and distribution of olive oil in this ancient province were growing exponentially during almost three centuries (cronologiaaa CITAR). As a results, hundred of amphora workshops were created to support this high demand. These workshops were located along the river Guadalquivir and its tributary Genil supplying from the riverine connectivity to the Mediterranean and Atlantic \citep{garcia_vargas_enrique_formal_2010}.

The majority of olive oil amphorae produced in this province and shipped thought the provinces belong to Dressel 20 type \citep{dressel,martin-kilcher_romischen_1994}. This amphora is commonly associated with transportation of Baetican olive oil during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body \citep{millet_anforas_1998}. 
The information of the stamps is shown in different forms and letter content and it seems that there was not a unique criteria (CITAR). Stamps was mostly formed for a code of three letters. There letters can appear in a abbreviated form or complete and they are known as \textit{Tria Nomina} \citep{berni_millet_amphora_1996}. 
The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the land-owners of the olive groves \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owners of the making-amphorae workshop (CITAR) or even a production counting system \citep{berni_millet_epigrafianforica_2008}. In any case, the use of these stamps defined somehow the system of working in the workshops.

>>>>

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. They allows us to highlight a part of mechanism of production and distribution of goods between different communities \citep{bevan_mediterranean_2014}.

@@

The production and distribution of olive oil in this ancient province were growing exponentially during almost three centuries \citep{remesal_concierto}. As a result, hundred of amphora workshops were created to support this high demand. These workshops were located along the river Guadalquivir and its tributary Genil supplying from the riverine connectivity to the Mediterranean and Atlantic \citep{garcia_vargas_enrique_formal_2010}.

The majority of olive oil amphorae produced in this province and shipped thought the provinces belong to Dressel 20 type \citep{dressel,martin-kilcher_romischen_1994}. This amphora is commonly associated with transportation of Baetican olive oil during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body \citep{millet_anforas_1998}. 
The information of the stamps is shown in different forms and letter content and it seems that there was not a unique criteria (CITAR                                           ). Stamps was mostly formed for a code of three letters. There letters can appear in a abbreviated form or complete and they are known as \textit{Tria Nomina} \citep{berni_millet_amphora_1996}. 
The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the land-owners of the olive groves \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owners of the making-amphorae workshop (CITAR) or even a production counting system \citep{berni_millet_epigrafianforica_2008}. In any case, the use of these stamps defined somehow the system of working in the workshops.
